Home Nighttime Cough Monitoring

### 2025-02-06 Lilah Melzer/cough_monitor_analysis.qmd
need to figure out missing CFQ-R dates

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor")
```

@@

```{r}
# CFQ-R Caregivers 6-13
# SAS code
# if nmiss (phys1, phys2, phys3, phys4, phys5, phys6) <= 3 then
# physical = (mean (phys1, phys2, phys3, phys4, phys5, phys6)-1)/3*100;
#
# if nmiss (emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14) <= 4 then
# emotion = (mean (emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14)-1)/3*100;
#
# if nmiss (social20, social21, social22, social23, social24, social25, social26) <= 3 then
# social = (mean (social20, social21, social22, social23, social24, social25, social26)-1)/3*100;
#
# if nmiss (eat15, eat17, eat19) <= 1 then
# eat = (mean(eat15, eat17, eat19)-1)/3*100;
#
# if nmiss (body27, body28, body29) <= 1 then
# body = (mean(body27, body28, body29)-1)/3*100;
#
# if nmiss (treat16, treat18, treat30) <= 1 then
# treat = (mean (treat16, treat18, treat30)-1)/3*100;
#
# if nmiss (resp31, resp32, resp33, resp34) <= 2 then
# respirat = (mean (resp31, resp32, resp33, resp34)-1)/3*100;
#
# if nmiss (digest35) = 0 then
# digest = (mean (digest35)-1)/3*100;

@@

# Do it!

@@

    sid, redcap_event_name:redcap_repeat_instance,
    cfq_r_p_1:cfq_r_p_44

@@

  mutate(across(cfq_r_p_1:cfq_r_p_44, ~ as.numeric(.x))) %>%

@@

@@

check <- left_join(
  df %>%

@@

      sid, redcap_event_name:redcap_repeat_instance,
      cfq_r_p_1:cfq_r_p_44

@@

  cfqr_parent_6_13 %>%
    select(sid, redcap_event_name:redcap_repeat_instance, physical:weight),
  join_by(
    sid, redcap_event_name, redcap_repeat_instrument,
    redcap_repeat_instance

@@

@@

write.csv(check, file = "./Data_Clean/cfqr_parent_6_13_check.csv", na = "", row.names = F)

cfqr_children_6_11 <- list(
  "cfq_r_y_1" = "phys1", "cfq_r_y_2" = "phys2", "cfq_r_y_3" = "phys3",
  "cfq_r_y_4" = "phys4", "cfq_r_y_5" = "phys5", "cfq_r_y_6" = "phys6",
  "cfq_r_y_7" = "emot7", "cfq_r_y_8" = "emot8", "cfq_r_y_9" = "emot9",
  "cfq_r_y_10" = "emot10", "cfq_r_y_11" = "emot11", "cfq_r_y_12" = "emot12",
  "cfq_r_y_13" = "emot13", "cfq_r_y_14" = "emot14", "cfq_r_y_15" = "eat15",
  "cfq_r_y_16" = "treat16", "cfq_r_y_17" = "eat17", "cfq_r_y_18" = "treat18",
  "cfq_r_y_19" = "eat19", "cfq_r_y_20" = "social20", "cfq_r_y_21" = "social21",
  "cfq_r_y_22" = "social22", "cfq_r_y_23" = "social23",
  "cfq_r_y_24" = "social24", "cfq_r_y_25" = "social25",
  "cfq_r_y_26" = "social26", "cfq_r_y_27" = "body27", "cfq_r_y_28" = "body28",
  "cfq_r_y_29" = "body29", "cfq_r_y_30" = "treat30", "cfq_r_y_31" = "resp31",
  "cfq_r_y_32" = "resp32", "cfq_r_y_33" = "resp33", "cfq_r_y_34" = "resp34",
  "cfq_r_y_35" = "digest35 "
)
cfqr_children_6_11 <-
  setNames(names(cfqr_children_6_11), cfqr_children_6_11)
cfqr_teens_adults <- list(
  "cfq_r_a_1" = "phys1", "cfq_r_a_2" = "phys2", "cfq_r_a_3" = "phys3",
  "cfq_r_a_4" = "phys4", "cfq_r_a_5" = "phys5", "cfq_r_a_6" = "vital6",
  "cfq_r_a_7" = "emot7", "cfq_r_a_8" = "emot8", "cfq_r_a_9" = "vital9",
  "cfq_r_a_10" = "vital10", "cfq_r_a_11" = "vital11", "cfq_r_a_12" = "emot12",
  "cfq_r_a_13" = "phys13", "cfq_r_a_14" = "eat14", "cfq_r_a_15" = "treat15",
  "cfq_r_a_16" = "treat16", "cfq_r_a_17" = "treat17", "cfq_r_a_18" = "health18",
  "cfq_r_a_19" = "phys19", "cfq_r_a_20" = "phys20", "cfq_r_a_21" = "eat21",
  "cfq_r_a_22" = "social22", "cfq_r_a_23" = "social23", "cfq_r_a_24" = "body24",
  "cfq_r_a_25" = "body25", "cfq_r_a_26" = "body26", "cfq_r_a_27" = "social27",
  "cfq_r_a_28" = "social28", "cfq_r_a_29" = "social29",
  "cfq_r_a_30" = "social30", "cfq_r_a_31" = "emot31", "cfq_r_a_32" = "health32",
  "cfq_r_a_33" = "emot33", "cfq_r_a_34" = "health34", "cfq_r_a_35" = "role35",
  "cfq_r_a_36" = "role36", "cfq_r_a_37" = "role37", "cfq_r_a_38" = "role38",
  "cfq_r_a_39" = "weight39", "cfq_r_a_40" = "resp40", "cfq_r_a_41" = "resp41",
  "cfq_r_a_42" = "resp42", "cfq_r_a_43" = "resp43", "cfq_r_a_44" = "resp44",
  "cfq_r_a_45" = "resp45", "cfq_r_a_46" = "resp46", "cfq_r_a_47" = "digest47",
  "cfq_r_a_48" = "digest48", "cfq_r_a_49" = "digest49", "cfq_r_a_50" = "eat50"
)
cfqr_teens_adults <-
  setNames(names(cfqr_teens_adults), cfqr_teens_adults)
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor")
```

@@

```{r}
# See SAS scoring instructions (from Quitter's CFQ-R website).docx for
# instructions

@@

# Do all the calculations!

@@

    sid, cfqr_caregivers_613_timestamp, cfq_r_p_1:cfq_r_p_44

@@

    Date = as.Date(cfqr_caregivers_613_timestamp),
    across(cfq_r_p_1:cfq_r_p_44, ~ as.numeric(.x))

@@

  select(sid, Date, physical:weight)
# Children aged 6 to 11
cfqr_children_6_11_names <- list(
  "cfq_r_y_1" = "phys1", "cfq_r_y_2" = "phys2", "cfq_r_y_3" = "phys3",
  "cfq_r_y_4" = "phys4", "cfq_r_y_5" = "phys5", "cfq_r_y_6" = "phys6",
  "cfq_r_y_7" = "emot7", "cfq_r_y_8" = "emot8", "cfq_r_y_9" = "emot9",
  "cfq_r_y_10" = "emot10", "cfq_r_y_11" = "emot11", "cfq_r_y_12" = "emot12",
  "cfq_r_y_13" = "emot13", "cfq_r_y_14" = "emot14", "cfq_r_y_15" = "eat15",
  "cfq_r_y_16" = "treat16", "cfq_r_y_17" = "eat17", "cfq_r_y_18" = "treat18",
  "cfq_r_y_19" = "eat19", "cfq_r_y_20" = "social20", "cfq_r_y_21" = "social21",
  "cfq_r_y_22" = "social22", "cfq_r_y_23" = "social23",
  "cfq_r_y_24" = "social24", "cfq_r_y_25" = "social25",
  "cfq_r_y_26" = "social26", "cfq_r_y_27" = "body27", "cfq_r_y_28" = "body28",
  "cfq_r_y_29" = "body29", "cfq_r_y_30" = "treat30", "cfq_r_y_31" = "resp31",
  "cfq_r_y_32" = "resp32", "cfq_r_y_33" = "resp33", "cfq_r_y_34" = "resp34",
  "cfq_r_y_35" = "digest35"

@@

cfqr_children_6_11_names <-
  setNames(names(cfqr_children_6_11_names), cfqr_children_6_11_names)
cfqr_children_6_11_reverse <- c(
  "phys1", "phys2", "phys3", "phys4", "phys5", "emot14", "treat18", "eat19",
  "social20", "social22", "social24", "social26"
# Do all the calculations
cfqr_children_6_11 <- df %>%

@@

    sid, cfqr_children_ages_611_timestamp, cfq_r_y_1:cfq_r_y_35
    Date = as.Date(cfqr_children_ages_611_timestamp),
    across(cfq_r_y_1:cfq_r_y_35, ~ as.numeric(.x))
  rename(all_of(unlist(cfqr_children_6_11_names))) %>%
  mutate(across(all_of(cfqr_children_6_11_reverse), ~ 5 - .x)) %>%
        sum(is.na(c(phys1, phys2, phys3, phys4, phys5, phys6))) <= 3,
        (mean(c(phys1, phys2, phys3, phys4, phys5, phys6)) - 1)

@@

        sum(is.na(c(emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14))) <= 4,
        (mean(c(emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14)) - 1)
    social =
        sum(is.na(c(social20, social21, social22, social23, social24, social25, social26))) <= 3,
        (mean(c(social20, social21, social22, social23, social24, social25, social26)) - 1)
        sum(is.na(c(eat15, eat17, eat19))) <= 1,
        (mean(c(eat15, eat17, eat19)) - 1)
        sum(is.na(c(body27, body28, body29))) <= 1,
        (mean(c(body27, body28, body29)) - 1)
        sum(is.na(c(treat16, treat18, treat30))) <= 1,
        (mean(c(treat16, treat18, treat30)) - 1)
        sum(is.na(c(resp31, resp32, resp33, resp34))) <= 2,
        (mean(c(resp31, resp32, resp33, resp34)) - 1)
        sum(is.na(c(digest35))) == 0,
        (mean(c(digest35)) - 1)

@@

  select(sid, Date, physical:digest)
# Teen/Adult version
cfqr_teens_adults_names <- list(
  "cfq_r_a_1" = "phys1", "cfq_r_a_2" = "phys2", "cfq_r_a_3" = "phys3",
  "cfq_r_a_4" = "phys4", "cfq_r_a_5" = "phys5", "cfq_r_a_6" = "vital6",
  "cfq_r_a_7" = "emot7", "cfq_r_a_8" = "emot8", "cfq_r_a_9" = "vital9",
  "cfq_r_a_10" = "vital10", "cfq_r_a_11" = "vital11", "cfq_r_a_12" = "emot12",
  "cfq_r_a_13" = "phys13", "cfq_r_a_14" = "eat14", "cfq_r_a_15" = "treat15",
  "cfq_r_a_16" = "treat16", "cfq_r_a_17" = "treat17", "cfq_r_a_18" = "health18",
  "cfq_r_a_19" = "phys19", "cfq_r_a_20" = "phys20", "cfq_r_a_21" = "eat21",
  "cfq_r_a_22" = "social22", "cfq_r_a_23" = "social23", "cfq_r_a_24" = "body24",
  "cfq_r_a_25" = "body25", "cfq_r_a_26" = "body26", "cfq_r_a_27" = "social27",
  "cfq_r_a_28" = "social28", "cfq_r_a_29" = "social29",
  "cfq_r_a_30" = "social30", "cfq_r_a_31" = "emot31", "cfq_r_a_32" = "health32",
  "cfq_r_a_33" = "emot33", "cfq_r_a_34" = "health34", "cfq_r_a_35" = "role35",
  "cfq_r_a_36" = "role36", "cfq_r_a_37" = "role37", "cfq_r_a_38" = "role38",
  "cfq_r_a_39" = "weight39", "cfq_r_a_40" = "resp40", "cfq_r_a_41" = "resp41",
  "cfq_r_a_42" = "resp42", "cfq_r_a_43" = "resp43", "cfq_r_a_44" = "resp44",
  "cfq_r_a_45" = "resp45", "cfq_r_a_46" = "resp46", "cfq_r_a_47" = "digest47",
  "cfq_r_a_48" = "digest48", "cfq_r_a_49" = "digest49", "cfq_r_a_50" = "eat50"

@@

cfqr_teens_adults_names <-
  setNames(names(cfqr_teens_adults_names), cfqr_teens_adults_names)
cfqr_teens_adults_reverse <- c(
  "vital6", "vital10", "phys13", "treat15", "treat17", "health18", "social23",
  "social28", "social30", "health32", "health34", "role35", "resp43"
# Do all the calculations
cfqr_teens_adults <- df %>%
    sid, cfqr_adolescents_and_adults_14_years_timestamp, cfq_r_a_1:cfq_r_a_50
    Date = as.Date(cfqr_adolescents_and_adults_14_years_timestamp),
    across(cfq_r_a_1:cfq_r_a_50, ~ as.numeric(.x))
  rename(all_of(unlist(cfqr_teens_adults_names))) %>%
  mutate(across(all_of(cfqr_teens_adults_reverse), ~ 5 - .x)) %>%
        sum(is.na(c(phys1, phys2, phys3, phys4, phys5, phys13, phys19, phys20))) <= 4,
        (mean(c(phys1, phys2, phys3, phys4, phys5, phys13, phys19, phys20)) - 1)
    role =
        sum(is.na(c(role35, role36, role37, role38))) <= 2,
        (mean(c(role35, role36, role37, role38)) - 1)
        sum(is.na(c(vital6, vital9, vital10, vital11))) <= 2,
        (mean(c(vital6, vital9, vital10, vital11)) - 1)
        sum(is.na(c(emot7, emot8, emot12, emot31, emot33))) <= 2,
        (mean(c(emot7, emot8, emot12, emot31, emot33)) - 1)
    social =
        sum(is.na(c(social22, social23, social27, social28, social29, social30))) <= 3,
        (mean(c(social22, social23, social27, social28, social29, social30)) - 1)
        sum(is.na(c(body24, body25, body26))) <= 1,
        (mean(c(body24, body25, body26)) - 1)
        sum(is.na(c(eat14, eat21, eat50))) <= 1,
        (mean(c(eat14, eat21, eat50)) - 1)
        sum(is.na(c(treat15, treat16, treat17))) <= 1,
        (mean(c(treat15, treat16, treat17)) - 1)
        sum(is.na(c(health18, health32, health34))) <= 1,
        (mean(c(health18, health32, health34)) - 1)
        sum(is.na(c(weight39))) == 0,
        (mean(c(weight39)) - 1)
        sum(is.na(c(resp40, resp41, resp42, resp44, resp45, resp46))) <= 3,
        (mean(c(resp40, resp41, resp42, resp44, resp45, resp46)) - 1)
        sum(is.na(c(digest47, digest48, digest49))) <= 1,
        (mean(c(digest47, digest48, digest49)) - 1)
  select(sid, Date, physical:digest)
# Write for checking
write.csv(df %>%
    sid, cfqr_caregivers_613_timestamp, cfq_r_p_1:cfq_r_p_44
  ), file = "~/cfqr_parent_6_13.csv", na = "", row.names = F)
write.csv(df %>%
    sid, cfqr_children_ages_611_timestamp, cfq_r_y_1:cfq_r_y_35
  ), file = "~/cfqr_children_6_11.csv", na = "", row.names = F)
write.csv(df %>%
    sid, cfqr_adolescents_and_adults_14_years_timestamp, cfq_r_a_1:cfq_r_a_50
  ), file = "~/cfqr_teens_adults.csv", na = "", row.names = F)
# Add to counts for plotting
cfqr_parent_6_13$sid <- as.numeric(cfqr_parent_6_13$sid)
cfqr_children_6_11$sid <- as.numeric(cfqr_children_6_11$sid)
cfqr_teens_adults$sid <- as.numeric(cfqr_teens_adults$sid)
agg_counts <- left_join(agg_counts, cfqr_parent_6_13)
agg_counts <- left_join(agg_counts, cfqr_children_6_11)
agg_counts <- left_join(agg_counts, cfqr_teens_adults)

## Respiratory scores

### Plots by participant

```{r}
#| message: false
#| warning: false
invisible(lapply(unique(agg_counts$sid), function(s) {
  d <- agg_counts[agg_counts$sid == s, ]
  diag <- d$Diagnosis[1]
  p <- ggplot(d, aes(
    x = Night, y = Coughs, group = factor(sid), color = Sick
  )) +
    geom_point() +
    geom_line() +
    theme_bw() +
    ylim(0, 50) +
    xlim(0, 150) +
    scale_color_manual(values = c("#377EB8", "#E41A1C")) +
    ggtitle(paste0("Participant ", s, " (", diag, ")"))
  if (s == 38) {
    p <- p + ylim(0, 270)
  }
  p2 <- ggplot(d[!is.na(d$respirat), ], aes(
    x = Night, y = respirat, group = factor(sid), color = Sick
  )) +
    geom_point() +
    geom_line() +
    theme_bw() +
    ylim(50, 100) +
    xlim(0, 150) +
    scale_color_manual(values = c("#377EB8", "#E41A1C")) +
    ggtitle(paste0("Participant ", s, " (", diag, ")"))
  cat("\n")
  cat("\n")
  print(p + p2 + plot_layout(guides = "collect"))
  cat("\n")
  cat("\n")
}))
```
